Article results

### 2022-07-11 analysis/article-results.Rmd
Checks with ggally
Remove univariable analyses + remove 1se attempts, start of trimming rmd

```{r objs}
tar_load(
  c(
    dat_combined,
    dat_to_impute,
    imps_all,
    candidate_predictors,
    model_formula,
    analysis_settings,
    validation_dev_lambdamin,
    validation_comb_lambdamin,
    validation_dev_lambda1se,
    validation_comb_lambda1se
  )
)

@@

## Univariable analyses

```{r univar-analyses}
univariate_analyses <- imps_all %>%

  # Only use separately imputed develop, valid and combined cohorts
  filter(imps_label != "imps_assess") %>%

  # Split each of three cohorts, and run analyses on each
  split(f = .$imps_label) %>% 
  map(.f = ~ {
    imps_univariate_ORs(
      outcome = "Mc_FailedFemoralApproach", 
      imps = split(.x, .x$.imp),
      predictors = c(
        candidate_predictors, 
        "ICA_nr_90orLarger",
        "OrigoStenosis50percent",
        "ICAIAtherosclerosis",
        "AngleAaInn_OR_AaCca"
      )
    )
  }) %>% 
  bind_rows(.id = "cohort")

# Make the table
univariate_table <- univariate_analyses %>% 
  select(cohort, term, estimate, `2.5 %`, `97.5 %`) %>%
  mutate(across(where(is.numeric), ~ round(.x, 2))) %>% 
  mutate(
    OR = paste0(estimate, " [", `2.5 %`, "-", `97.5 %`, "]"),
    cohort = factor(
      cohort, 
      levels = c("imps_dev", "imps_valid", "imps_combined"),
      labels = c("develop_cohort", "validation_cohort", "combined_cohort")
    )
  ) %>%

  # Spread and set column order
  pivot_wider(names_from = cohort, values_from = OR, id_cols = term) %>% 
  select(term, develop_cohort, validation_cohort, combined_cohort)

knitr::kable(univariate_table)
```

### Interaction analyses

```{r inters-univar}
# Cohort interactions (Should probably be ommitted from manuscript)
dat_interactions <- imps_all %>% 
  filter(imps_label %in% c("imps_dev", "imps_valid"))

interactions_table <- imps_univariate_ORs(
  outcome = "Mc_FailedFemoralApproach",
  imps = split(x = dat_interactions, f = dat_interactions$.imp),
  predictors = paste0(candidate_predictors, " * imps_label") # imp_label is surrogate for cohort
) %>%

  # Keep only interaction terms - keep  p-values
  filter(grepl(x = term, pattern = "\\:")) %>% 
  select(term, p.value)

knitr::kable(interactions_table)
```

@@

>>>>

```{r objs}
tar_load(
  c(
    dat_combined,
    dat_to_impute,
    imps_all,
    candidate_predictors,
    model_formula,
    analysis_settings,
    validation_dev_lambdamin,
    validation_comb_lambdamin
  )
)

@@

@@

dat_combined |> 
  select(candidate_predictors, dataset) |>  
    #Mc_FailedFemoralApproach, dataset) |> 
  GGally::ggpairs(
    aes(col = dataset, fill = dataset)
  )
